How is experience transformed into memory?

### 2018-09-27 paper/main.tex
minor edits needed for nature submission
minor figure cleanup in illustrator

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}

@@

%\doublespacing

@@

\begin{abstract}
How our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.  Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.  We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.  We apply this approach to a naturalistic memory experiment which had participants view and recount a video.  We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.  We also identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
\end{abstract}

@@

\subsection*{Experimental design and data collection}
Data were collected by \cite{ChenEtal17}.  In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).  The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.  After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the [episode] in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better. They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it. Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.

@@

\subsection*{Data availability}
The behavioral and fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}

@@

\doublespacing
\linenumbers

@@

\begin{abstract}
The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.  Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.  We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.  We apply this approach to a naturalistic memory experiment which had participants view and recount a video.  We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.  We also identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
\end{abstract}

@@

\subsection*{Experimental design and data collection}
Data were collected by \cite{ChenEtal17}.  In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).  The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.  After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the [episode] in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better. They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it. Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.  The experimental protocol was approved by Princeton University's Institutional Review Board.

@@

\subsection*{Data and code availability}
The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.  The behavioral data and all of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
